%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingSimple}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Warren Christian} \\ \vspace{1pt}
    \small US Citizen $|$ \href{mailto:wlchrist00@gmail.com}{\underline{warren.christian@wsu.edu}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/wlchrist}} $|$
    \href{https://github.com/...}{\underline{github.com/wlchrist}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Washington State University}{Pullman, WA}
      {Bachelor of Science in Computer Science}{Expected May 2026}
       \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Computer Architecture, Operating Systems, Data Structures \& Algorithms, Machine Learning}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
{Embedded Engineering Intern}{Nov. 2023 -- Present}
{Schweitzer Engineering Laboratories (SEL)}{Pullman, WA}
\resumeItemListStart
\resumeItem {Collaborate daily with hardware engineers to validate \textbf{C/C++ firmware} on proprietary power relay hardware, integrating ad-hoc network discovery protocols with \textbf{RTOS} stacks.}
\resumeItem {Develop modular, multi-threaded software components utilizing semaphores and asynchronous event handling for high-reliability embedded systems.}
\resumeItem {Designed and implemented \textbf{test harnesses} and unit testing frameworks to validate protocol behavior, improving system reliability for production-level firmware.}
\resumeItem{Utilize serial telemetry and \textbf{Linux} debugging tools to isolate hardware-software interface issues during development cycles.}
\resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Technical Projects}
  \resumeSubHeadingListStart
  
    \resumeSubheadingSimple{Automated Film Development Machine (Hardware/Embedded)}{July 2024}
  \resumeItemListStart
    \resumeItem{Authored \textbf{PCB and wiring diagrams}, assembled and \textbf{soldered hardware} components for an \textbf{ESP32}-based control system using \textbf{C/C++}.}
    \resumeItem{Programmed firmware to coordinate stepper motors, pumps, and temperature sensors; implemented \textbf{UART} telemetry and error-detection for hardware fault handling.}
    \resumeItem{Produced full documentation and a test harness to validate hardware repeatability across development cycles.}
  \resumeItemListEnd

    \resumeSubheadingSimple{Swift-NIO FTP Protocol Pipeline}{March 2025}
\resumeItemListStart
  \resumeItem{Built a low-level \textbf{networking pipeline} in Swift using \textbf{SwiftNIO}, implementing command parsing and data transfer according to RFC standards.}
  \resumeItem{Developed custom channel handlers for encoding/decoding and request routing, gaining deep experience in TCP/IP and networking technologies.}
\resumeItemListEnd

      \resumeSubheadingSimple{Robotics Drone Software (AgAID Research Institute)}{May 2025}
      \resumeItemListStart
        \resumeItem{Developed drone-based mapping software using \textbf{Flutter} and 3D imaging algorithms for agricultural infrastructure analysis.}
      \resumeItemListEnd

    \resumeSubheadingSimple{AI Snowpack Prediction (WSU Hackathon Winner)}{Dec. 2024}
      \resumeItemListStart
        \resumeItem{Developed a deep learning model (LSTM) for climate forecasting using \textbf{Python}, \textbf{PyTorch}, and university HPC resources.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Hardware \& Systems}{: RTOS, Embedded C/C++, PCB Design, Soldering, Computer Architecture, UART, SPI, I2C} \\
     \textbf{Languages \& Scripting}{: C/C++, Python (Automation), Shell Scripting (Bash), Swift, SQL} \\
     \textbf{Networking \& OS}{: Linux Proficiency, TCP/IP, CCNA, Swift-NIO, VS Code, Git, Azure DevOps} \\
     \textbf{AI/ML}{: PyTorch, Pandas, TensorFlow, Optuna} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}